## Predictive Modeling of Tropical Forest Community Structure

---

### Purpose of the project
To develop a model projecting the forest community structure in the future given the current community structure (species composition and number of individuals in seed, seedling, sapling and adult stages)

### Output of the model
an array with matrices of populations structure of different species as components.

For example: If the community has s species, the output will be an array with s matrices, each matrix has t rows (t = time (year)) with four columns reporting number of individuals in each stage (seed, seedling, sapling, adult).  Below is the first component of the array: the population structure of species 1

```{r }
[ , , 1]

	seed	seedling	sapling	adult
1	Ns11	Nsl11	Nsa11	Na11
2	Ns12	Nsl12	Nsa12	Na12
…	…	…	…	…
T	Ns1t	Nsl1t	Nsa1t	Na1t
	
```

When:
	
	Ns11 = Number of seeds of species 1 at year 1
	Nsl12 = Number of seedling of species 1 at year 2


### Inputs for the model
#### 1. Matrix of community structure at time 0, columns are life stages and rows are species

```{r }

	seed	seedli	sapli	adult
1	Ns10	Nsl10	Nsa10	Na10
2	Ns20	Nsl20	Nsa20	Na20
…	…	…	  …	…
s	Nss0	Nsls0	Nsat0	Nat0

```

#### 2. Matrix of mortality rates and transition rates of each species in the community

Seed : germination rate (Gs) When 1-Gs is  mortality rate(Ms)
Seedling : mortality (Msl), transition rate (Gsl)
Sapling : mortality (Msa), transition rate (Gsa)
Adult : mortality (Ma), Reproduction rate (Ra), Maximum size

```{r }

Ns1 = Na0*Ra
Nsl1 = Nsl0 - Nsl0*Msl + Ns0*Gs
Nsa1 = Nsa0 – Nsa0*Msa – Nsa0*Gsa + Nsl0*Gsl
Na1 = Na0 – Na0*Ma + Nsa*Gsa

```
The matrix will have 7 columns for 7 parameters and n rows for n species

```{r }

	Ra	Gs	Msl	Gsl	Msa	Gsa	Ma
sp1	Ra1	Gs1	Msl1	Gls1	Msa1	Gsa1	Ma1
Sp2	..	..	..	..	..	..	..
spn	Ran	Gsn	Msln	Gsln	Msan	Gsan	Man

```

#### 3. Time (t)

### R-CODING

1. Create a function called "para.m" that takes parameter input and put them into a matrix
called "para.mat"

```{r }

para.m = function(Ra, Gs, Msl, Gsl, Msa, Gsa, Ma){

v.mat = c(0,Gs,0,0,0,(1-Msl),Gsl,0,0,0,(1-Msa-Gsa),Gsa,Ra,0,0,(1-Ma))
para.mat = matrix(data = v.mat, nrow = 4, ncol=4, byrow=TRUE)
return(para.mat)

}

```

2. Create a function called "para.ar" that takes each row of 4x7 matrix and use para.m 
to create array of 4x4 matrices

```{r }

para.ar = function(x){
	
	n.sp = nrow(x)
	sp.para = array(data=NA, dim=c(4,4,n.sp))
	
	for (i in 1:n.sp){
		tmp = x[i,]
		sp.para[,,i] = para.m(tmp[1],tmp[2],tmp[3],tmp[4],tmp[5],tmp[6],tmp[7])
	}
	return(sp.para)
}

```

3. Create a function that takes a vector and a matrix and multiply those two

```{r }

	pop.t.cal = function(sp1,para.mat){
	pop.t = sp1 %*% para.mat
	return (pop.t)
	}

```

4. Create a function that takes the coummunity matrix, moratilty&transition matrix(4x7) 
and time (t) and calculate population structure at each year

```{r }
com.struct = function(t0.com,mor.tran,t){

	tmp.sp.para = para.ar(mor.tran) #array of parameters matrix of each species
	
	n.sp = nrow(t0.com)
	
	struct.arr = array(data=NA, dim=c(n.sp,4,t+1)) #array of community structure at each time step
	
	struct.arr[,,1] = t0.com # first one is at year 0
	
	for (i in 2:(t+1)) {
	
		t0 = struct.arr[,,(i-1)]
	
		t1 = matrix(data=NA, nrow=n.sp, ncol=4)
	
		for (j in 1:n.sp) {
		
			a = t0
			b = tmp.sp.para[,,j]
		
			t1[j,] = pop.t.cal(a[j,],b)
		}
	
	struct.arr[,,i] = t1
		
	}
	return(struct.arr)
}

```