## Predictive Modeling of Tropical Forest Community Structure

---

### Purpose of the project
To develop a model projecting the forest community structure in the future given the current community structure (species composition and number of individuals in seed, seedling, sapling and adult stages)

### Output of the model
an array with matrices of populations structure of different species as components.

For example: If the community has s species, the output will be an array with s matrices, each matrix has t rows (t = time (year)) with four columns reporting number of individuals in each stage (seed, seedling, sapling, adult).  Below is the first component of the array: the population structure of species 1

```{r }
[ , , 1]

	seed	seedling	sapling	adult
1	Ns11	Nsl11	Nsa11	Na11
2	Ns12	Nsl12	Nsa12	Na12
…	…	…	…	…
T	Ns1t	Nsl1t	Nsa1t	Na1t
	
```

When:
	
	Ns11 = Number of seeds of species 1 at year 1
	Nsl12 = Number of seedling of species 1 at year 2


### Inputs for the model
#### 1. Matrix of community structure at time 0, columns are life stages and rows are species

```{r }

	seed	seedling	sapling	adult
1	Ns10	Nsl10		Nsa10	Na10
2	Ns20	Nsl20		Nsa20	Na20
…	…		…			…		…
s	Nss0	Nsls0		Nsat0	Nat0

```

#### 2. Matrix of mortality rates and transition rates of each species in the community

Seed : germination rate (Gs) When 1-Gs is  mortality rate(Ms)
Seedling : mortality (Msl), transition rate (Gsl)
Sapling : mortality (Msa), transition rate (Gsa)
Adult : mortality (Ma), Reproduction rate (Ra), Maximum size

```{r }

Ns1 = Na0*Ra
Nsl1 = Nsl0 - Nsl0*Msl + Ns0*Gs
Nsa1 = Nsa0 – Nsa0*Msa – Nsa0*Gsa + Nsl0*Gsl
Na1 = Na0 – Na0*Ma + Nsa*Gsa

```
The matrix will have 7 columns for 7 parameters and n rows for n species

```{r }

	Ra	Gs	Msl	Gsl	Msa	Gsa	Ma
sp1	Ra1	Gs1	Msl1	Gls1	Msa1	Gsa1	Ma1
Sp2	..	..	..	..	..	..	..
spn	Ran	Gsn	Msln	Gsln	Msan	Gsan	Man

```

#### 3. Time (t)
